### 2016-07-06 version0.0/intro0.0.tex
adding prelude to into. section

\chapter{Introduction}
\label{chap:intro}

\section{Overview}
Understanding the processes that go into the formation and evolution of stars and stellar systems is crucial in the study of the chemical composition and structure formation of the universe. Stars are also central to the formation of planetary systems and are where the ingredients for life were formed. The energy provided by stars is necessary to maintain the life on planets. The study of the formation and evolution of the Sun, and more generally that of stars, would help us understand more about our origin and the future of our Solar System. This is one of the main reasons that the study of stellar structure and evolution has been a central topic in astronomy and astrophysics for decades.

In order to completely understand the formation and evolution of galaxies from early universe to the current epoch, the knowledge of the formation of stars is necessary. Star formation determines the structure and evolution of galaxies, by transforming gas into stars. Moreover, the knowledge of star formation is essential to understanding the origin of planetary systems. The physical process of star formation is naturally complex. Therefore, the basis for a theory of star formation requires a strong foundation of empirical data or observations.

In a galaxy like our own, star formation begins with condensation of giant molecular clouds (GMCs, $\sim 10^7$ M$_{\odot})$ in the interstellar medium (ISM) which is due to gravitational instabilities. The interplay of turbulence and magnetic field with self-gravity is believed to be responsible for the formation of clumps within GMCs. Some of these clumps develop into self-gravitating cores, which have a similar distribution to stellar initial mass function (IMF) while turbulence and magnetic field play central roles in defining this distribution. Numerical simulations have shown that magnetic fields in the cores become super-critical and collapse\citep{Basu97}. In the process of  collapsing, an accretion disk is formed and significant magnetic flux is lost while the star also gradually loses its angular momentum. Powerful winds are magnetocentrifugally driven from the surface of the disk and turn into a jet-like flow due to magnetic hoops stresses \citep{Shu94}. This wind flows from the protostellar core and sweeps up gas into a massive molecular outflow. Massive stars form from massive cores, which are highly energised. These stars are highly luminous, therefore, they ionize their surrounding gas into \hii regions. GMCs lose much of their original mass due to photo-evaporation. Most of the mass lost returns to the diffuse interstellar medium and completes the cycle of star formation, which then starts a new cycle (see~\cite{McKee07} for more detail).

The study of star formation has been an ongoing process and extends into the present era. The physical processes of star formation can be studied by direct observation. For more than 50 years, the numerical simulations, the empirical and theoretical laws, which describe the star formation rate have been investigated; nevertheless, their results have never been precise. Formation of stars is a complicated process. Various phenomena affect the collapse of molecular clouds and star formation which include the environment of the star-forming region, chemical compositions, the initial mass distribution of gas, gas accretion and cooling, H$_2$ formation, etc. Thus to fully understand this intricate process, many theories have been proposed and numerical simulations are carried out.

Despite the complex physical properties, fortunately there are empirical scaling laws to relate the star formation to other properties of galaxies. The most well-known of these scaling laws is the relation between the surface density of the star formation rate (SFR) and the gas surface density, which is known as the Kennicutt-Schmidt (KS) law \citep{Schmidt59, Kennicutt98a}. Similar to KS law, another scaling relation was derived which is a linear scaling between the total SFR and the mass of molecular gas (refer to the review by \cite{Elmgrenn11}). More recently, \cite{Shi11} derived another scaling relation, which relates the surface density of the SFR of galaxies to both gas surface density and the stellar mass.

In this chapter, we present the observational review of measuring the star formation rate and other properties that affect measuring and scaling the SFR in nearby galaxies. In $\S$~\ref{chap:sfr} we discuss measuring the star formation rate. A discussion of the ISM is presented in $\S$~\ref{chap:ISM}, followed by a discussion of the measurement of the stellar mass in $\S$~\ref{chap:starrmass}. In $\S$~\ref{chap:metal} we talk about effect of metallicity on SFR. The current issues about studying star formation and its relation to other properties of a galaxy and the present project are discussed in $\S$~\ref{chap:cipp}.

%-----------------------------------------------------
% Chapter: SFR
%-----------------------------------------------------
\section{Star Formation Rate}
\label{chap:sfr}

Understanding formation of stars leads to understanding galaxy formations. Characterisation of the star formation processes, such as the total SFR and the initial mass function of a galaxy, is necessary in examining its structure formation \citep{McKee07}. The main problem is that measuring the SFR is not trivial and depends on the galaxy morphology, metallicity, IMF, the spatial resolution of a target system, etc. There is a large number of review papers in the literature on how stars form and how their formation is traced. From a theoretical perspective, one can refer to the classic picture of the theory of star formation as reviewed by \cite{Shu87} and more recently by \citep{McKee07}. From an observational standpoint, star formation is discussed by \cite{Kennicutt98b, Kewley02, Bell03, Calzetti07, Calzetti08, Calzetti10, Calzetti13, Kennicutt07, Kennicutt09, Boquien10, Hao11, Kennicutt12}.

@@

As mentioned in section ~\ref{sec: imf}, using different IMFs leads to having different SFR calibrations. From table~\ref{table1} it is clear that changing the IMF affects the H${\alpha}$ SFR calibration more than other SFR calibrations. This effect is more than four times larger than UV SFR calibrations because newly-formed stars having up to $\sim 5$ M$_{\odot}$ emit more strongly at UV radiations; however, significant amounts of ionising photons are produced by stars more massive than $\sim 20$ M$_{\odot}$. Furthermore, reaching an asymptotic value takes longer for more massive stars (10 Myr for the upper mass limit of 30 M$_{\odot}$ versus 6 Myr for 100 M$_{\odot}$). Therefore, changes in the H${\alpha}$ SFR calibration constant are more pronounced, while for UV and TIR calibration constants are fairly close to each other. On the other hand, using the mean stellar mass for the Kroupa IMF $(<$M$> \sim 0.6$ M$_{\odot})$ yields less than $10\%$ difference between using the upper mass limit of 100 M$_{\odot}$ and 30 M$_{\odot}$. As a result, calibrations derived with the mean stellar mass of a system are more accurate than those that are based on tracing the most massive stars \citep{Calzetti13}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%chapter: ISM
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Interstellar Medium}
\label{chap:ism}

Interstellar medium (ISM) is referred to the space between stars in a galaxy, which is full of a thin hydrogen and helium gas and small amounts of heavier elements called metals. These elements can have neutral, ionized, or molecular forms and can be in gas phase or solid state. The gas and dust in the ISM are heated by interstellar radiation field and cool through a variety of line and continuum processes which usually depend on the local physical conditions. The ISM has a huge impact on the formation and evolution of stars. Since stars are born in the ISM and release their material into the ISM when they reach the end of their evolution, studying the ISM is essential in the understanding of the formation and evolution of stars.

Considering the effects of the ISM on studying the SFR is important for two main reasons. First, stars are born from the gas; therefore, for scaling the star-formation rate in a galaxy, knowledge on the amount of gas is necessary. The other impact is that gas and dust in the ISM absorb the UV or optical emission from stars and re-emit it in the IR, or scatter the stellar light. Thus for tracing the star-forming region, the effect of dust must be taken into account, otherwise the SFR might be underestimated. 
\subsection{Molecular clouds}
\subsection{Ionized regions}
\subsection{Dust}

\subsection{Map of the ISM}
\label{sec: ismmap}

A map of the total gas in the ISM is produced by direct observations of the gas or using interstellar dust as a tracer. Neutral and molecular hydrogen are the most common elements in the ISM. Therefore, for producing the map of the total gas in galaxies, maps of these two components can be added together and multiplied by a constant factor to account for heavier elements which are mostly He. Another way to do the mapping is assuming that the ratio of total gas and dust is constant across a galaxy, and convert dust observations to the map of total gas.

\begin{figure}[h]
\label{fig: mco}
\centering
\includegraphics[width=16cm]{../image_intro/mvirial_lco.eps}
\caption{Relation between The Virial mass and CO luminosity for the Milky Way (dots), M33 (open circles), m31 (triangles), and IC 10 (squares) clouds. The Virial masses measured from selected high spatial resolution CO observations are shown. The extragalactic molecular clouds are very similar to those in the Milky Way. Adapted from \cite{Young91}}
\end{figure}

\subsection{Extinction and Attenuation}
\label{sec: ism}
In this section, dust ``attenuation" and ``extinction" will be introduced and their effects on measuring the SFR will be briefly discussed. More advanced and detailed discussions on this topic is out of the scope of this paper; and for more information one can refer to the review by \citep{Calzetti01}.

Extinction happens when there is a combination of both absorption and scattering of radiation by dust. The distribution of the dust that lies between a source and the observer is irrelevant to the total extinction value because the source is a background point source (left panel of Fig.{~\ref{fig:duste}}).

Attenuation refers to the effect of dust with embedded light sources distributed throughout. The dust itself can be clumpy or smooth\citep{Calzetti13}. In this situation the relative location of the dust and light sources affect the net absorbed and scattered light, and that happens because both the light sources and the dust have extended distributions (right panel of Fig.{~\ref{fig:duste}}). Dust scattering's effect depends on whether it is in or out of the line of sight. When the dust is in the line of sight, attenuation will make the emerging light dimmer and the SED will be bluer. This is the typical situation that comes across when studying galaxies or extended regions within galaxies.

\begin{figure}[h]
\label{fig:duste}
\centering
\includegraphics[width=16cm]{../image_intro/dustextinction}
\caption{The cartoon of: a) a point source behind a screen of dust, a typical situation to have an extinction; and b) the distribution of stars and clumps of dust, typical system, when attenuation effect is observed. Adopted from \cite{Calzetti13}}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%chapter :stellar mass
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Stellar Mass}
\label{chap:starmass}
One of the most fundamental physical parameters which describes the present state of the galaxies is stellar mass. It was pointed out that stellar mass is linked with the structure and star formation history of disc galaxies \citep{Gavvazi96} and all morphologies \citep{Scodeggio02}. In order to determine stellar population in spiral galaxies, the mean stellar mass density of a galaxy may be a more basic parameter than the total stellar mass \citep{Bell00}. \cite{Kauffmann03} tested that on more than 100,000 galaxies observed by Sloan Digital Sky Survey \citep[SDSS;][]{York00}. They also showed that these results are applied for all morphological types.

@@

Having two independent methods to measure stellar mass helps to compare the results and check whether there are any systematic differences. Comparing the results from measuring stellar mass in stellar clusters shows there is no huge difference. Comparing the results from measuring stellar mass within galaxies shows that the deferences are on the order of a few x10 percent, so one should be more careful to model subtleties \citep{McLaughlin05}. In the following we address the approaches of measuring stellar mass in galaxies in more detail.

@@

Measuring the stellar mass from equation~\ref{equ:eskew} is limited to the nearby galaxies, and might break down for high star forming regions, moreover, this equation have not tested on regions with different metallicity. Thus there is no calibration regarding variation in  metallicity \citep{Eskew12}. On the other hand equations~\ref{equ: zhu1} -~\ref{equ: zhu3} have been derived from a large sample of galaxies, and was tested on different type of regions and galaxies. Beside they can be used for more distanced galaxy as well as nearby galaxies \citep{Zhu10}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%chapter: KS law
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Scaling the SFR Using Schmidt-Kennicut Law}

% The first idea about scaling the star formation rate on the galaxy scale was proposed as a connection between the total star formation rate and the mass of interstellar gas. \cite{Schmidt59} assumed the constant IMF of stars, $\Psi (M)$, a stellar lifetime function {$T(M$)}, and a star formation rate {$SFR(T)$} and derived the star formation rate (SFR) over the history of the Milky Way. He scaled SFR with a power {\it n} of the gas mass, $M_{gas}$. Then $SFR(T)\Sigma_{M}(M) = c[M_{gas}(t)]^n$, for a summation over all stellar type $M$. A power law relation between surface densities of star formation and gas is known as the Schmidt law and is written as:
% \begin{equation}
% \Sigma_{SFR} \propto \Sigma_{gas}^n
% \end{equation}
% where $\Sigma_{SFR}$ is surface density of star formation, $\Sigma_{gas}$ is the surface density of gas in a galaxy and, {\it n} is the power index.

% Following \cite{Schmidt59}, many groups worked on the scaling relation between the surface density of star formation, and the surface density of gas. \cite{Buat89} assumed the constant H$_2$/CO ratio and a \cite{Scalo86} initial mass function for the Milky Way. They measured SFR from the UV flux corrected and included molecular and atomic gas to derive the correlation between the star formation rate and the gas surface density. Another major work in that year was \cite{Kennicutt89}. By using H$\alpha$ emission for star formation, and HI and CO as a tracer of gas with constant H$_2$/CO, for more than 15 galaxies, he determined the average H$\alpha$ flux can be scaled with the average gas surface density to a power between 1 and 2.  To get better results he calculated star formation rate both as a function of galactocentric radius and averaged over whole galaxy disks. He also showed that the correlation is more accurate with using only HI as a tracer of gas.

% A decade later, \cite{Kennicutt98a} examined another group of galaxies. He used H$\alpha$, HI and CO observations of 61 normal spiral galaxies and 36 starburst galaxies and showed that the disk-average SFRs and gas densities for this samples are well represented by the Schmidt law with the power of $1.4 \pm 0.15$. Using this power index, the Schmidt law can be rewritten as:

% \begin{equation}
% \Sigma_{SFR} \propto \Sigma_{gas}^{1.4\pm0.15}
% \end{equation}
% which is often referred to as the Kennicutt-Schmidt (KS) law.

% In more recent studies, \cite{Kennicutt08} investigated the local star formation law in M51 with 0.5-2 kpc resolution. For the SFR he used pa${\alpha}$ and $24\mu$m + H${\alpha}$ lines and for gas density he used constant conversion factor for CO to H$_2$. He found a correlation, from the radial variation of both SFR and gas surface density, with an index of $1.56 \pm 0.04$. He could not find any correlation between SFR and HI only clouds, but the correlation with the molecular cloud was about the same as the total gas.
% It should be noted that the KS law can not be applied for the whole range of gas densities. In parallel studies, the star formation threshold was introduced and it was pointed out that calculated SFR is much lower than the value predicted by the KS law at low gas densities $( < 1-10\sim$ M$_{\odot}$ pc$^{-2})$ e.g. in regions far outside the optical disk \citep[e.g.,][]{Martin01, Bigiel08}

% The Schmidt-Kennicutt scaling relation for star formation is valid for different types of galaxies both in the local universe \citep[e.g.,][]{Kennicutt98a, Bigiel08} and at high-Z \citep[e.g.,][]{Genzel10}, but it is strange that they only consider the effect of gas component while in reality various ISM and stellar objects affect the processes of formation of stars. Current proposed Schmidt relations, do not include the effects of metallicity \citep{Gnedin10}, dust grains, radiation shielding of H$_2$ regions \citep[for a review, see][]{Hollenbach99}, and stellar gravitational effects, as they only invoke the gas component.  Existing stars which form over the whole galaxy's life time are the reason for many of the processes mentioned above. As an example the gas angular momentum can be removed or nuclear SFRs can be increased by the gravitational effects of stellar bars in normal galaxies \citep[e.g.,][]{Sersic67}.

% \cite{Hunter98} have shown that, in low surface brightness galaxies the SFR density is only related to the stellar mass density. Also similar relations between stellar masses and SFR densities are seen within galaxies by \cite{Ryder94}, \cite{Hunter04} and recently by \cite{Leroy08} for specific galaxy types or limited density ranges. \cite{Shi11} found a tight relationship between stellar mass surface density, SFR and gas surface density by studying on a large sample of galaxies. They showed this relation as a power law relation and referred to it as the extended Schmidt law:

% \begin{equation}
% \Sigma_{SFR} \propto \Sigma_{gas}^{\alpha} \Sigma_{star}^{\beta}
% \end{equation}
% where $\Sigma_{SFR}$ is SFR surface density, $\Sigma_{gas}$ and $\Sigma_{star}$ are gas mass and stellar surface density. $\alpha$ and $\beta$ are the power law indexes.  They showed that this relation not only predicts SFR as well as the KS law for galaxies and spatially resolved regions ($\sim$1 kpc sizes) where the KS law works, but also is acceptable for low surface brightness galaxies and regions where the KS law fails.

% \begin{figure}[h]
% \label{fig:duste}
% \centering
% \includegraphics[width=16cm]{../image_intro/schmidtvsextended}
% \caption{Comparing The extended Schmidt law (a) and the Kennicutt-Schmidt relationship (b) for predicting the SFR. The solid and dotted lines are the best fit and observed 1-$\sigma$ scatter, respectively. The fit to the KS law (right panel) is done excluding LSB and early type galaxies. Adapted from \cite{Shi11}.}
% \end{figure}

>>>>

\chapter{Introduction}
\label{chap:intro}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%Overview%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Prelude}
\label{sec: overview}
%what do we have inside galaxies:
% stuff we don't care about because they don't have a big contribution on the SED 1) planets; 2) black holes 3) dark matter
Inside every galaxy, there are millions of stars, planets, black holes, and high amount of dust and gas which all affect each others' formation, evolution and extinction.
There are also dark matter inside every galaxy, which to the best our knowledge only has gravitational effect on the galaxies.%add ref.s
All the information we can obtain from galaxies other than our owns are implanted in their light. % now we can detect gravitational wave which is not part of the SEDs, right?
Light emitted from young and evolved stars, and dust and gas in the space between stars have the most contribution on spectral energy distributions (SEDs) of galaxies.
We cannot detect any contribution from planets and black holes on SEDs due to their low intensity or the limitation of our detectors.
Therefore, with properly modeling observed features in SEDs we can extract information about evolution of stars, dust and gas inside galaxies.

%stars
Arguably, stars are the main component of normal galaxies.
They control the chemical composition and structure of galaxies by transforming gas into new born stars and by transforming death stars to the gas.
They are also central to the formation and evolution of planetary systems.
The energy provided by stars is necessary to create and maintain the life on planets. 
The study of the formation and evolution of the Sun, and more generally that of stars, would help us understand more about our origin and the future of our Solar System.
Furthermore, in order to completely understand the formation and evolution of galaxies from early universe to the current epoch, the knowledge of the formation and evolution of stars is necessary. 
As a result, the study of stellar formation and evolution has been a central topic in astronomy and astrophysics for decades.

%ISM 1)Gas 2)dust
There could be a galaxy without stars (i.e. dark galaxies~\citep[][and references therein]{Cantalupo12}), but there will never be a galaxy without gas.
Gas and dust in galaxies can be found in the space between stars that is called interstellar medium (ISM) which is full of low density gaseous clouds with neutral or ionized atoms and/or molecules, and microscopic dust grains.
The gas and dust in ISM are heated by interstellar radiation field and cool through a variety of line and continuum processes which usually depend on the local physical conditions. 
Effect of ISM in stellar formation is undeniable; ISM provides raw material for formation of stars~\citep[e.g.][]{Kennicutt08,Bigiel08}.
Studying ISM is not only essential for understanding of the formation of stars but also it is necessary for interpretation of stellar evolution in that stars release their material into ISM when they reach at the end of their evolution.

% Metallicity
Metallicity, which is defined as the ratio of abundance of metal to the abundance of hydrogen atom, affects formation and evolution of stars indisputably.
In a galaxy like our own, star formation begins with condensation of giant molecular clouds (GMCs, $\sim 10^7$ M$_{\odot})$ in ISM which is due to gravitational instabilities. 
The interplay of turbulence and magnetic field with self-gravity is believed to be responsible for the formation of clumps within GMCs. 
Some of these clumps develop into self-gravitating cores, which have a similar distribution to stellar initial mass function (IMF) while turbulence and magnetic field play central roles in defining this distribution (see~\cite{McKee07} for more detail).
\cite{Walch11} showed that in case of the large scale turbulence the amount of metallicity on star formation is negligible, but if turbulence is decaying  metallicity has high impact and stabilizing self-gravitating cores.
Metals also play an important role on heating, cooling and ionizing processes in ISM. %%ADD ref.
Since cooling is one of the main reason of condensation of GMCs~\citep[e.g.][]{Maio07}, in low metallicity regions star formation may be suppressed. %Sahar: should I talk about metallicity in stars and their relation with age?

%what does SED look like?
Our primary source of information for galaxies, specifically unresolved ones, is their SEDs.
Broadly speaking, young and hot stars emit most of their light in Ultraviolet (UV) wavelengths, evolved stellar population show themselves in optical and near-Infrared (NIR) emission and gas and dust heated by stellar emission are bright in Mid-IR (MIR) or far-IR (FIR) wavelengths.
Therefore, UV-to-IR SEDs contains valuable information about stellar evolution and their ISM. 
Other wavelengths regimes in SEDs (i.e. X-ray, radio), that are dominated by processes such as active galactic nuclei, quasars, and supernovae shock, are beyond the scope of this thesis.
general shape of SEDs mirrors the morphological type of galaxies; starburst galaxies, which have high star formation rate (SFR), emit bulk of their energy in UV, while light of quiescent galaxies are dominated by optical and IR emission 
Detail information about age of stellar populations and other properties of galaxies can be determine by properly modelling of galaxy SEDs.

 %how do you model it? %SED model CIGALE %Population synthesis ----> SFR, stellar mass
Stellar population synthesis method, which sums stellar spectra of a galaxy to produces its spectrum, is widely utilized from 1970s~\citep[e.g.][]{Tinsley72,Searle73} to model SEDs of galaxies.
A through SED model must include stellar population models~\citep[e.g.][]{Bruzual93,Bruzual03,Maraston05}, stellar emission and dust attenuation~\citep[e.g.][]{Calzetti00,Dopita05}, dust grains emission such as polycyclic aromatic hydrocarbons~\citep[PAHs; e.g.][and references therein]{Tielens08}, and IR emission from gas and dust~\citep[e.g.][]{Chary01,Dale02,Lagache03,Lagache04,Smith07a,Draine07}, to fit the observed SEDs.
Many groups modelled SEDs for different type of galaxies and created templates of SEDs. (for more information see review of \cite{Walcher11} on fitting of SEDs and references therein).
Since the physical parameters of templates generated by the SED models are known, we can find properties of observed galaxies by fitting their SEDs using the templates.
Code Investigating GALaxy Emission ({\em CIGALE})~\citep{Noll09} is one example of codes that find best SED fittings.
It combines some of the SED models to find best SED fitting for given observed data in the rest-frame of UV-to-IR and find physical properties of galaxies such as SFR, Stellar mass and dust attenuation.

Formation of stars is a complicated process and directly affect on galaxies evolution. 
Various phenomena affect the collapse of molecular clouds and star formation which include the environment of the star-forming region, chemical compositions, the initial mass distribution of gas, gas accretion and cooling, H$_2$ formation, etc. 
For more than 50 years, the numerical simulations, the empirical and theoretical laws, which describe the star formation rate have been investigated; nevertheless, their results have never been precise. 
There are empirical scaling laws to relate the star formation to other properties of galaxies. 
The most well-known of these scaling laws is the relation between the surface density of the star formation rate (SFR) and the gas surface density, which is known as the Kennicutt-Schmidt (KS) law~\citep{Schmidt59, Kennicutt98a}. 
Similar to KS law, another scaling relation was derived which is a linear scaling between the total SFR and the mass of molecular gas (refer to reviews~\cite{Elmgrenn11, Kennicutt12}).

In this chapter, we present a review of observational method of measuring the star formation rate and the main properties that affect measuring and scaling the SFR. A discussion of the ISM, its role on star formation is presented in $\S$~\ref{sec: ism_intro}, In $\S$~\ref{sec: sfr_intro} we discuss measuring the star formation rate, followed by a discussion of the measurement of the stellar mass in $\S$~\ref{sec: starmass_intro}. The current issues about studying star formation and its relation to other properties of a galaxy are discussed in $\S$~\ref{sec: pre_intro}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%ISM%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Interstellar Medium}
\label{sec: ism_intro}
%how do we observe it
%what the observation tell us
% how do we measure the dust and gas
ISM in galaxies is a complex system with wide range of structures, but this structures can be divided into two main components: Gas and Dust.
Gas in ISM of galaxies is mostly made of hydrogen and helium with 1 per cent of heavier elements (metals), and can be in the forms of clouds or diffuse regions.
Gas clouds contains molecular clouds, cold neutral hydrogen (\hi~) or hot \hi~clouds, and diffuse gas can be either \hii~(ionized hydrogen) regions or hot intercloud mediums.
Dust mostly contains silicate, graphite grains can be seen in dark clouds or galactic cirrus.
%Among these regions in ISM, molecular clouds, \hii~regions and dust clouds have important role in understanding star formation in galaxies. 
Emission lines from atoms or ions (i.e \hii~regions) in a hot gas, lines from molecules in cold clouds and 21~cm emission of \hi~are the main observing signatures of the gas in the ISM of galaxies.
Dust can be observed directly through FIR and sub-mm observation or indirectly through their extinction and attenuation effect (see Sec.~\ref{sec: extinction}).

%%observing \hii region
%what do we observe
%how the line is created
%why it is important for star formation

%%observing molecular clouds
%what do we observe
%how the line is created
%why it is important for star formation

%%observing molecular clouds
%what do we observe
%how the line is created
%why it is important for star formation

%%observingdust
%what do we observe
%how the line is created
%why it is important for star formation

\hii~regions are generally associate with star formation 
%\subsection{Ionized regions}

%\subsection{Molecular clouds}
Molecular clouds in ISM are cold ($\sim10$ K) and dense ($ 50<n<500$ cm$^{-3}$)~\cite{Bolato08}.
These clouds are cold and dense enough to form simple molecules; hence the name, but they are surrounded by cloud of atomic gas~\cite{Kennicutt12}.
The area, where the hydrogen is in a molecular form but the carbon is in atomic state, is called the transition region, dark gas, photo-dissociation regions or photon-dominated regions~\citep[e.g.][]{van88,Hollenbach99}.

%\subsection{Dust}

\subsection{Map of the ISM}
\label{sec: ismmap}
A map of the total gas in the ISM is produced by direct observations of the gas or using interstellar dust as a tracer. 
Neutral and molecular hydrogen are the most common elements in the ISM. Therefore, for producing the map of the total gas in galaxies, maps of these two components can be added together and multiplied by a constant factor to account for heavier elements which are mostly He. Another way to do the mapping is assuming that the ratio of total gas and dust is constant across a galaxy, and convert dust observations to the map of total gas.

\begin{figure}
\label{fig: mco}
\centering
\includegraphics[width=16cm]{../image_intro/mvirial_lco.eps}
\caption{Relation between The Virial mass and CO luminosity for the Milky Way (dots), M33 (open circles), m31 (triangles), and IC 10 (squares) clouds. The Virial masses measured from selected high spatial resolution CO observations are shown. The extragalactic molecular clouds are very similar to those in the Milky Way. Adapted from \cite{Young91}}
\end{figure}

\subsection{Extinction and Attenuation}
\label{sec: extinction}
In this section, dust ``attenuation" and ``extinction" will be introduced and their effects on measuring the SFR will be briefly discussed. More advanced and detailed discussions on this topic is out of the scope of this paper; and for more information one can refer to the review by \citep{Calzetti01}.

Extinction happens when there is a combination of both absorption and scattering of radiation by dust. The distribution of the dust that lies between a source and the observer is irrelevant to the total extinction value because the source is a background point source.

Attenuation refers to the effect of dust with embedded light sources distributed throughout. The dust itself can be clumpy or smooth\citep{Calzetti13}. In this situation the relative location of the dust and light sources affect the net absorbed and scattered light, and that happens because both the light sources and the dust have extended distributions. Dust scattering's effect depends on whether it is in or out of the line of sight. When the dust is in the line of sight, attenuation will make the emerging light dimmer and the SED will be bluer. This is the typical situation that comes across when studying galaxies or extended regions within galaxies.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%SFR%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{SFR}
\label{sec: sfr_intro}
%beside the normal ones; add SFR based on PAHs, add SFR from SED
Understanding formation of stars leads to understanding galaxy formations. Characterisation of the star formation processes, such as the total SFR and the initial mass function of a galaxy, is necessary in examining its structure formation \citep{McKee07}. The main problem is that measuring the SFR is not trivial and depends on the galaxy morphology, metallicity, IMF, the spatial resolution of a target system, etc. There is a large number of review papers in the literature on how stars form and how their formation is traced. From a theoretical perspective, one can refer to the classic picture of the theory of star formation as reviewed by \cite{Shu87} and more recently by \citep{McKee07}. From an observational standpoint, star formation is discussed by \cite{Kennicutt98b, Kewley02, Bell03, Calzetti07, Calzetti08, Calzetti10, Calzetti13, Kennicutt07, Kennicutt09, Boquien10, Hao11, Kennicutt12}.

@@

As mentioned in section ~\ref{sec: imf}, using different IMFs leads to having different SFR calibrations. From table~\ref{table1} it is clear that changing the IMF affects the H${\alpha}$ SFR calibration more than other SFR calibrations. This effect is more than four times larger than UV SFR calibrations because newly-formed stars having up to $\sim 5$ M$_{\odot}$ emit more strongly at UV radiations; however, significant amounts of ionising photons are produced by stars more massive than $\sim 20$ M$_{\odot}$. Furthermore, reaching an asymptotic value takes longer for more massive stars (10 Myr for the upper mass limit of 30 M$_{\odot}$ versus 6 Myr for 100 M$_{\odot}$). Therefore, changes in the H${\alpha}$ SFR calibration constant are more pronounced, while for UV and TIR calibration constants are fairly close to each other. On the other hand, using the mean stellar mass for the Kroupa IMF $(<$M$> \sim 0.6$ M$_{\odot})$ yields less than $10\%$ difference between using the upper mass limit of 100 M$_{\odot}$ and 30 M$_{\odot}$. As a result, calibrations derived with the mean stellar mass of a system are more accurate than those that are based on tracing the most massive stars \citep{Calzetti13}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%Stellar Mass%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Stellar mass}
\label{sec: starmass_intro}
One of the most fundamental physical parameters which describes the present state of the galaxies is stellar mass. It was pointed out that stellar mass is linked with the structure and star formation history of disc galaxies \citep{Gavvazi96} and all morphologies \citep{Scodeggio02}. In order to determine stellar population in spiral galaxies, the mean stellar mass density of a galaxy may be a more basic parameter than the total stellar mass \citep{Bell00}. \cite{Kauffmann03} tested that on more than 100,000 galaxies observed by Sloan Digital Sky Survey \citep[SDSS;][]{York00}. They also showed that these results are applied for all morphological types.

@@

Having two independent methods to measure stellar mass helps to compare the results and check whether there are any systematic differences. Comparing the results from measuring stellar mass in stellar clusters shows there is no huge difference. Comparing the results from measuring stellar mass within galaxies shows that the differences are on the order of a few x10 percent, so one should be more careful to model subtleties \citep{McLaughlin05}. In the following we address the approaches of measuring stellar mass in galaxies in more detail.

@@

Measuring the stellar mass from equation~\ref{equ:eskew} is limited to the nearby galaxies, and might break down for high star forming regions, moreover, this equation have not tested on regions with different metallicity. Thus there is no calibration regarding variation in  metallicity \citep{Eskew12}. On the other hand equations~\ref{equ: zhu1} -~\ref{equ: zhu3} have been derived from a large sample of galaxies, and was tested on different type of regions and galaxies. Beside they can be used for more distanced galaxy as well as nearby galaxies \citep{Zhu10}. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%Preview%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Preview}
\label{sec: pre_intro}
%Thesis questions.

\addcontentsline{toc}{section}{Bibliography}
\bibliographystyle{apj.bst} 
\bibliography{ref_intro}
